---
title: "Homework 1"
author: "Atakan Demirkan"
date: "4 Nisan 2021"
output: html_document
---
# Part 1

```{r, message=FALSE,warning=FALSE}
library("readxl")
library("zoo")
```

```{r}
basepath<-"C:\\Users\\aadem\\OneDrive\\Desktop\\"
```


## CPI Data of Turkey
### Obtaining Data

Firstly, I obtaining data from Electronic Data Delivery System of TCMB to my computer. I read the data via read.table function.

```{r}
CPI <- read_excel(path=paste(basepath,"CPI.xlsx",sep="")) 
```

### Preparing Data

```{r}
CPI<-transform(CPI,CPI=as.numeric(CPI),Date=as.yearmon(Date))
```


### Plotting

Secondly, I made a line chart of CPI Data with plot function.

```{r}
plot(CPI,type = "o", col = "red", xlab = "Date", ylab = "CPI",
   main = "TURKEY CPI")
```

### Analysis
  In CPI, there is a very clear increasing trend.

## USDTRY Data

### Obtaining Data

```{r}
USDTRY <- read_excel(path=paste(basepath,"USDTRY.xlsx",sep="")) 
                      
```
### Preparing Data

```{r}
USDTRY<-transform(USDTRY,USDTRY=as.numeric(USDTRY),Date=as.yearmon(Date))
```

### Plotting

Secondly, I made a line chart of CPI Data with plot function.

```{r}
plot(USDTRY,type = "o", col = "blue", xlab = "Date", ylab = "USDTRY",
   main = "USDTRY")
```

### Analysis

## XAUTRY Data

### Obtaining Data

```{r}
XAUTRY <- read_excel(path=paste(basepath,"XAUTRY.xlsx",sep="")) 
                      
```
### Preparing Data

```{r}
XAUTRY<-transform(XAUTRY,XAUTRY=as.numeric(XAUTRY),Date=as.yearmon(Date))
```

### Plotting

Secondly, I made a line chart of CPI Data with plot function.

```{r}
plot(XAUTRY,type = "o", col = "green", xlab = "Date", ylab = "XAUTRY",
   main = "XAUTRY")
```
```

# Part 2
## Turkish IPO Market and Reatil Investors


