---
title: "IE 360 HW4-5"
author: "Atakan Demirkan"
date: "3 Temmuz 2021"
output: html_document
---


# Introduction

### Description

Everyday, millions of people purchase many different items via online shopping websites. As Internet evolves throughout years, online shopping became one of the most important sectors around world. Trendyol.com is the largest mobile commerce company in Turkey and the MENA region selling more than 70 million items per year. Considering the wide product spectrum and strong sales of Trendyol, the correct decisions should be made with great precision in order to continue the operation successfully. Deciding how many products to sell in the future is one of the most important of these decisions. Forecasting the sales quantity of a product for an online retail is a challenging task. The aim of this assignment is to build a forecasting model for the sales quantities of 9 different products. 

### Required Libraries

Firstly, I initiated required libraries.

```{r, message=FALSE, warning=FALSE}
library(jsonlite)
library(httr)
library(data.table)
library(stats)
library(forecast)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(GGally)
library(corrplot)
library(dplyr)
library(tidyr)
library(readxl)
library(zoo)
library(corrplot)
library(hrbrthemes)
library(viridis)
```

### Reading Data

```{r}
get_token <- function(username, password, url_site){
  
  post_body = list(username=username,password=password)
  post_url_string = paste0(url_site,'/token/')
  result = POST(post_url_string, body = post_body)
  
  # error handling (wrong credentials)
  if(result$status_code==400){
    print('Check your credentials')
    return(0)
  }
  else if (result$status_code==201){
    output = content(result)
    token = output$key
  }
  
  return(token)
}

get_data <- function(start_date='2020-03-20', token, url_site){
  
  post_body = list(start_date=start_date,username=username,password=password)
  post_url_string = paste0(url_site,'/dataset/')
  
  header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
  result = GET(post_url_string, header, body = post_body)
  output = content(result)
  data = data.table::rbindlist(output)
  data[,event_date:=as.Date(event_date)]
  data = data[order(product_content_id,event_date)]
  return(data)
}


send_submission <- function(predictions, token, url_site, submit_now=F){
  
  format_check=check_format(predictions)
  if(!format_check){
    return(FALSE)
  }
  
  post_string="list("
  for(i in 1:nrow(predictions)){
    post_string=sprintf("%s'%s'=%s",post_string,predictions$product_content_id[i],predictions$forecast[i])
    if(i<nrow(predictions)){
      post_string=sprintf("%s,",post_string)
    } else {
      post_string=sprintf("%s)",post_string)
    }
  }
  
  submission = eval(parse(text=post_string))
  json_body = jsonlite::toJSON(submission, auto_unbox = TRUE)
  submission=list(submission=json_body)
  
  print(submission)
  # {"31515569":2.4,"32737302":2.4,"32939029":2.4,"4066298":2.4,"48740784":2.4,"6676673":2.4, "7061886":2.4, "73318567":2.4, "85004":2.4} 
  
  if(!submit_now){
    print("You did not submit.")
    return(FALSE)      
  }
  
  
  header = add_headers(c(Authorization=paste('Token',token,sep=' ')))
  post_url_string = paste0(url_site,'/submission/')
  result = POST(post_url_string, header, body=submission)
  
  if (result$status_code==201){
    print("Successfully submitted. Below you can see the details of your submission")
  } else {
    print("Could not submit. Please check the error message below, contact the assistant if needed.")
  }
  
  print(content(result))
  
}

check_format <- function(predictions){
  
  if(is.data.frame(predictions) | is.data.frame(predictions)){
    if(all(c('product_content_id','forecast') %in% names(predictions))){
      if(is.numeric(predictions$forecast)){
        print("Format OK")
        return(TRUE)
      } else {
        print("forecast information is not numeric")
        return(FALSE)                
      }
    } else {
      print("Wrong column names. Please provide 'product_content_id' and 'forecast' columns")
      return(FALSE)
    }
    
  } else {
    print("Wrong format. Please provide data.frame or data.table object")
    return(FALSE)
  }
  
}

# this part is main code
subm_url = 'http://46.101.163.177'

u_name = "Group11"
p_word = "UcZ2v9SNRuqpQL62"
submit_now = FALSE

username = u_name
password = p_word

token = get_token(username=u_name, password=p_word, url=subm_url)
data = get_data(token=token,url=subm_url)
data

date_to_forecast="2021-06-26"

```

```{r}
my_data= read.csv("C:\\Users\\aadem\\OneDrive\\Desktop\\ProjectRawData.csv")
my_data=as.data.table(my_data)
my_data$event_date=ymd(my_data$event_date)
str(my_data)
summary(my_data)
```





# Task 1 & Task 2

## Product 1 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product1= my_data[my_data$product_content_id==31515569,]
product1=(product1[order(product1$event_date),])
prd1_add=data[data$product_content_id==31515569,]
prd1_add=prd1_add[event_date>="2021-06-01",]
prd1_add
product1=rbind(product1,prd1_add)
```

### Visualizing

The plot of the series is shown below. When the data is visually analyzed, it is difficult to talk about any seasonality. In some periods, deviations from the normal levels were observed. Any promotion may have been made on these dates.

```{r}
(ggplot(product1,aes(x=event_date,y=sold_count))+
  geom_line()+
  theme_minimal()+
  labs(title="Product 1",y="Sold Count", x="Event Date"))
```


### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. Autocorrelation values above the critical value were observed in some lag values.

```{r}
acf(product1$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr1_ts_w=ts(product1$sold_count, frequency=7,start = min(product1$event_date))
pr1_ts_decompose_wa=decompose(pr1_ts_w)
pr1_ts_decompose_wm=decompose(pr1_ts_w, type="multiplicative")
plot(pr1_ts_decompose_wa)
plot(pr1_ts_decompose_wm)
```

```{r}
pr1_ts_m=ts(product1$sold_count, frequency=30,start = min(product1$event_date))
pr1_ts_decompose_ma=decompose(pr1_ts_m)
pr1_ts_decompose_mm=decompose(pr1_ts_m, type="multiplicative")
plot(pr1_ts_decompose_ma)
plot(pr1_ts_decompose_mm)
```

### ARIMA

```{r , echo=FALSE}
acf(pr1_ts_decompose_wm$random,na.action=na.pass)
pacf(pr1_ts_decompose_wm$random,na.action=na.pass)
```  
  
I use auto.arima function to deseasonalized and detrended parts of the products to determine the best models. 

```{r}
pr1_auto=auto.arima(pr1_ts_decompose_wm$random)
pr1_auto
residuals(pr1_auto)
pr1_fitted = pr1_ts_decompose_wm$random - residuals(pr1_auto)
pr1_fitted_transformed = pr1_fitted*pr1_ts_decompose_wm$seasonal*pr1_ts_decompose_wm$trend
plot(pr1_ts_w, xlab="Date", ylab="Sold Count")
points(pr1_fitted_transformed,type="l", col=2, lty=5)
pr1_predictions=cbind(sold_count=pr1_ts_w,fitted=pr1_fitted_transformed)
pr1_predictions=as.data.table(pr1_predictions)
pr1_predictions$date=product1$event_date 
ggplot(pr1_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")
```

## Product 2 

### Data Adjustments

I added new data, sorted observations from old to new and remove repeated elements.

```{r}
product2= my_data[my_data$product_content_id==32737302,]
product2=(product2[order(product2$event_date),])
prd2_add=data[data$product_content_id==32737302,]
prd2_add=prd2_add[event_date>="2021-06-01",]
prd2_add
product2=rbind(product2,prd2_add)
product2=unique(product2)
```

### Visualizing

The plot of the series is shown below.It is observed that sales are small in winter months and high in the summer. Sales are highest in the beginning of summer. 

```{r}
(ggplot(product2,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 2",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. Autocorrelation values above the critical value were observed in almost all lag values.

```{r}
acf(product2$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr2_ts_w=ts(product2$sold_count, frequency=7,start = min(product2$event_date))
pr2_ts_decompose_wa=decompose(pr2_ts_w)
pr2_ts_decompose_wm=decompose(pr2_ts_w, type="multiplicative")
plot(pr2_ts_decompose_wa)
plot(pr2_ts_decompose_wm)
```

```{r}
pr2_ts_m=ts(product2$sold_count, frequency=30,start = min(product2$event_date))
pr2_ts_decompose_ma=decompose(pr2_ts_m)
pr2_ts_decompose_mm=decompose(pr2_ts_m, type="multiplicative")
plot(pr2_ts_decompose_ma)
plot(pr2_ts_decompose_mm)
```

### ARIMA

```{r}
pr2_auto=auto.arima(pr2_ts_decompose_wa$random)
pr2_auto
residuals(pr2_auto)
pr2_fitted = pr2_ts_decompose_wa$random - residuals(pr2_auto)
pr2_fitted_transformed = pr2_fitted+pr2_ts_decompose_wa$seasonal+pr2_ts_decompose_wa$trend
plot(pr2_ts_w, xlab="Date", ylab="Sold Count")
points(pr2_fitted_transformed,type="l", col=2, lty=5)
pr2_predictions=cbind(sold_count=pr2_ts_w,fitted=pr2_fitted_transformed)
pr2_predictions=as.data.table(pr2_predictions)
pr2_predictions=cbind(pr2_predictions,date=product2$event_date)
ggplot(pr2_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")
```

## Product 3 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product3= my_data[my_data$product_content_id==32939029,]
product3=(product3[order(product3$event_date),])
prd3_add=data[data$product_content_id==32939029,]
prd3_add=prd3_add[event_date>="2021-06-01",]
prd3_add
product3=rbind(product3,prd3_add)
```

### Visualizing

The plot of the series is shown below.It is observed that there is a mean shift starting from the spring of 2021. Variance of the series is not constant.

```{r}
(ggplot(product3,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 3",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. Autocorrelation values above the critical value were observed in almost all lag values.

```{r}
acf(product3$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr3_ts_w=ts(product3$sold_count, frequency=7,start = min(product3$event_date))
pr3_ts_decompose_wa=decompose(pr3_ts_w)
pr3_ts_decompose_wm=decompose(pr3_ts_w, type="multiplicative")
plot(pr3_ts_decompose_wa)
plot(pr3_ts_decompose_wm)
```

```{r}
pr3_ts_m=ts(product3$sold_count, frequency=30,start = min(product3$event_date))
pr3_ts_decompose_ma=decompose(pr3_ts_m)
pr3_ts_decompose_mm=decompose(pr3_ts_m, type="multiplicative")
plot(pr3_ts_decompose_ma)
plot(pr3_ts_decompose_mm)
```

### ARIMA

```{r}
pr3_auto=auto.arima(pr3_ts_decompose_wm$random)
pr3_auto
residuals(pr3_auto)
pr3_fitted = pr3_ts_decompose_wm$random - residuals(pr3_auto)
pr3_fitted_transformed = pr3_fitted*pr3_ts_decompose_wm$seasonal*pr3_ts_decompose_wm$trend
plot(pr3_ts_w, xlab="Date", ylab="Sold Count")
points(pr3_fitted_transformed,type="l", col=2, lty=5)
pr3_predictions=cbind(sold_count=pr3_ts_w,fitted=pr3_fitted_transformed)
pr3_predictions=as.data.table(pr3_predictions)
pr3_predictions$date=product3$event_date
ggplot(pr3_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")

```



## Product 4 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product4= my_data[my_data$product_content_id==4066298,]
product4=(product4[order(product4$event_date),])
prd4_add=data[data$product_content_id==4066298,]
prd4_add=prd4_add[event_date>="2021-06-01",]
prd4_add
product4=rbind(product4,prd4_add)
```

### Visualizing

The plot of the series is shown below.Seasonality is observed in 2020, however there is not any seasonality in 2021.Variance of the series is not constant. There are several short periods with high sales.

```{r}
(ggplot(product4,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 4",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product4$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr4_ts_w=ts(product4$sold_count, frequency=7,start = min(product4$event_date))
pr4_ts_decompose_wa=decompose(pr4_ts_w)
pr4_ts_decompose_wm=decompose(pr4_ts_w, type="multiplicative")
plot(pr4_ts_decompose_wa)
plot(pr4_ts_decompose_wm)
```

```{r}
pr4_ts_m=ts(product4$sold_count, frequency=30,start = min(product4$event_date))
pr4_ts_decompose_ma=decompose(pr4_ts_m)
pr4_ts_decompose_mm=decompose(pr4_ts_m, type="multiplicative")
plot(pr4_ts_decompose_ma)
plot(pr4_ts_decompose_mm)
```

### ARIMA

```{r}
pr4_auto=auto.arima(pr4_ts_decompose_wm$random)
pr4_auto
residuals(pr4_auto)
pr4_fitted = pr4_ts_decompose_wm$random - residuals(pr4_auto)
pr4_fitted_transformed = pr4_fitted*pr4_ts_decompose_wm$seasonal*pr4_ts_decompose_wm$trend
plot(pr4_ts_w, xlab="Date", ylab="Sold Count")
points(pr4_fitted_transformed,type="l", col=2, lty=5)
pr4_predictions=cbind(sold_count=pr4_ts_w,fitted=pr4_fitted_transformed)
pr4_predictions=as.data.table(pr4_predictions)
pr4_predictions$date=product4$event_date
ggplot(pr4_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")

```

## Product 5 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product5= my_data[my_data$product_content_id==48740784,]
product5=(product5[order(product5$event_date),])
prd5_add=data[data$product_content_id==48740784,]
prd5_add=prd5_add[event_date>="2021-06-01",]
prd5_add
product5=rbind(product5,prd5_add)
product5=product5[event_date>"2020-09-28"]
```

### Visualizing

The plot of the series is shown below.This product is mostly sold in the winter of 2020. There are a few periods with small sold counts. Recently there is a small increase in the sales possibly due to summer discounts.

```{r}
(ggplot(product5,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 5",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product5$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr5_ts_w=ts(product5$sold_count, frequency=7,start = min(product5$event_date))
pr5_ts_decompose_wa=decompose(pr5_ts_w)
pr5_ts_decompose_wm=decompose(pr5_ts_w, type="multiplicative")
plot(pr5_ts_decompose_wa)
plot(pr5_ts_decompose_wm)
```

```{r}
pr5_ts_m=ts(product5$sold_count, frequency=30,start = min(product5$event_date))
pr5_ts_decompose_ma=decompose(pr5_ts_m)
pr5_ts_decompose_mm=decompose(pr5_ts_m, type="multiplicative")
plot(pr5_ts_decompose_ma)
plot(pr5_ts_decompose_mm)
```

### ARIMA


## Product 6 
### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product6= my_data[my_data$product_content_id==6676673,]
product6=(product6[order(product6$event_date),])
prd6_add=data[data$product_content_id==6676673,]
prd6_add=prd6_add[event_date>="2021-06-01",]
prd6_add
product6=rbind(product6,prd6_add)
```

### Visualizing

The plot of the series is shown below.There are several mean-shifts and the variance of the series is not constant. 

```{r}
(ggplot(product6,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 6",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product6$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr6_ts_w=ts(product6$sold_count, frequency=7,start = min(product6$event_date))
pr6_ts_decompose_wa=decompose(pr6_ts_w)
pr6_ts_decompose_wm=decompose(pr6_ts_w, type="multiplicative")
plot(pr6_ts_decompose_wa)
plot(pr6_ts_decompose_wm)
```

```{r}
pr6_ts_m=ts(product6$sold_count, frequency=30,start = min(product6$event_date))
pr6_ts_decompose_ma=decompose(pr6_ts_m)
pr6_ts_decompose_mm=decompose(pr6_ts_m, type="multiplicative")
plot(pr6_ts_decompose_ma)
plot(pr6_ts_decompose_mm)
```

### ARIMA

```{r}
pr6_auto=auto.arima(pr6_ts_decompose_wm$random)
pr6_auto
residuals(pr6_auto)
pr6_fitted = pr6_ts_decompose_wm$random - residuals(pr6_auto)
pr6_fitted_transformed = pr6_fitted*pr6_ts_decompose_wm$seasonal*pr6_ts_decompose_wm$trend
plot(pr6_ts_w, xlab="Date", ylab="Sold Count")
points(pr6_fitted_transformed,type="l", col=2, lty=5)
pr6_predictions=cbind(sold_count=pr6_ts_w,fitted=pr6_fitted_transformed)
pr6_predictions=as.data.table(pr6_predictions)
pr6_predictions$date=product6$event_date
ggplot(pr6_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")
```

## Product 7 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product7= my_data[my_data$product_content_id==7061886,]
product7=(product7[order(product7$event_date),])
prd7_add=data[data$product_content_id==7061886,]
prd7_add=prd7_add[event_date>="2021-06-01",]
prd7_add
product7=rbind(product7,prd7_add)
```

### Visualizing

The plot of the series is shown below.Mean of the data is not constant. There are several high-sale periods therefore variance is not constant.

```{r}
(ggplot(product7,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 7",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product7$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr7_ts_w=ts(product7$sold_count, frequency=7,start = min(product7$event_date))
pr7_ts_decompose_wa=decompose(pr7_ts_w)
pr7_ts_decompose_wm=decompose(pr7_ts_w, type="multiplicative")
plot(pr7_ts_decompose_wa)
plot(pr7_ts_decompose_wm)
```

```{r}
pr7_ts_m=ts(product7$sold_count, frequency=30,start = min(product7$event_date))
pr7_ts_decompose_ma=decompose(pr7_ts_m)
pr7_ts_decompose_mm=decompose(pr7_ts_m, type="multiplicative")
plot(pr7_ts_decompose_ma)
plot(pr7_ts_decompose_mm)
```

### ARIMA

```{r}
pr7_auto=auto.arima(pr7_ts_decompose_wm$random)
pr7_auto
residuals(pr7_auto)
pr7_fitted = pr7_ts_decompose_wm$random - residuals(pr7_auto)
pr7_fitted_transformed = pr7_fitted*pr7_ts_decompose_wm$seasonal*pr7_ts_decompose_wm$trend

plot(pr7_ts_w, xlab="Date", ylab="Sold Count")
points(pr7_fitted_transformed,type="l", col=2, lty=5)

pr7_predictions=cbind(sold_count=pr7_ts_w,fitted=pr7_fitted_transformed)
pr7_predictions=as.data.table(pr7_predictions)
pr7_predictions$date=product7$event_date

ggplot(pr7_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")+ theme_minimal()+
  labs(title="Product 7 Fitted Values ", x="Date", y="Sold Count")
```

## Product 8 

### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product8= my_data[my_data$product_content_id==73318567,]
product8=(product8[order(product8$event_date),])
prd8_add=data[data$product_content_id==73318567,]
prd8_add=prd8_add[event_date>="2021-06-01",]
prd8_add
product8=rbind(product8,prd8_add)
```

### Visualizing

The plot of the series is shown below. There are not any sales before winter of 2021, this period is removed in modeling. During the winter sales counts are varying however there is an increasing trend in summer. Variance of the sales during the summer and winter are not constant.

```{r}
(ggplot(product8,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 8",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product8$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr8_ts_w=ts(product8$sold_count, frequency=7,start = min(product8$event_date))
pr8_ts_decompose_wa=decompose(pr8_ts_w)
pr8_ts_decompose_wm=decompose(pr8_ts_w, type="multiplicative")
plot(pr8_ts_decompose_wa)
plot(pr8_ts_decompose_wm)
```

```{r}
pr8_ts_m=ts(product8$sold_count, frequency=30,start = min(product8$event_date))
pr8_ts_decompose_ma=decompose(pr8_ts_m)
pr8_ts_decompose_mm=decompose(pr8_ts_m, type="multiplicative")
plot(pr8_ts_decompose_ma)
plot(pr8_ts_decompose_mm)
```

### ARIMA

```{r}
pr8_auto=auto.arima(pr8_ts_decompose_wm$random)
pr8_auto
residuals(pr8_auto)
pr8_fitted = pr8_ts_decompose_wm$random - residuals(pr8_auto)
pr8_fitted_transformed = pr8_fitted*pr8_ts_decompose_wm$seasonal*pr8_ts_decompose_wm$trend

plot(pr8_ts_w, xlab="Date", ylab="Sold Count")
points(pr8_fitted_transformed,type="l", col=2, lty=5)

pr8_predictions=cbind(sold_count=pr8_ts_w,fitted=pr8_fitted_transformed)
pr8_predictions=as.data.table(pr8_predictions)
pr8_predictions$date=product8$event_date

ggplot(pr8_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")+ theme_minimal()+
  labs(title="Product 8 Fitted Values ", x="Date", y="Sold Count")
```

## Product 9 
### Data Adjustments

I added new data and sorted observations from old to new.

```{r}
product9= my_data[my_data$product_content_id==85004,]
product9=(product9[order(product9$event_date),])
prd9_add=data[data$product_content_id==85004,]
prd9_add=prd9_add[event_date>="2021-06-01",]
prd9_add
product9=rbind(product9,prd9_add)
```

### Visualizing

The plot of the series is shown below.Sales have different means in 2020 and 2021. Variance is not constant in both years.

```{r}
(ggplot(product9,aes(x=event_date,y=sold_count))+
    geom_line()+
    theme_minimal()+
    labs(title="Product 9",y="Sold Count", x="Event Date"))
```

### Analyze Seasonality

In addition to visual analysis, I also used the acf function to test seasonality. 

```{r}
acf(product9$sold_count,50)
```

### Decomposition

I made multiplicative and additive decomposition in weekly and monthly level.

```{r}
pr9_ts_w=ts(product9$sold_count, frequency=7,start = min(product9$event_date))
pr9_ts_decompose_wa=decompose(pr9_ts_w)
pr9_ts_decompose_wm=decompose(pr9_ts_w, type="multiplicative")
plot(pr9_ts_decompose_wa)
plot(pr9_ts_decompose_wm)
```

```{r}
pr9_ts_m=ts(product9$sold_count, frequency=30,start = min(product9$event_date))
pr9_ts_decompose_ma=decompose(pr9_ts_m)
pr9_ts_decompose_mm=decompose(pr9_ts_m, type="multiplicative")
plot(pr9_ts_decompose_ma)
plot(pr9_ts_decompose_mm)
```

### ARIMA

```{r}
pr9_auto=auto.arima(pr9_ts_decompose_wm$random)
pr9_auto
residuals(pr9_auto)
pr9_fitted = pr9_ts_decompose_wm$random - residuals(pr9_auto)
pr9_fitted_transformed = pr9_fitted*pr9_ts_decompose_wm$seasonal*pr9_ts_decompose_wm$trend

plot(pr9_ts_w, xlab="Date", ylab="Sold Count")
points(pr9_fitted_transformed,type="l", col=2, lty=5)

pr9_predictions=cbind(sold_count=pr9_ts_w,fitted=pr9_fitted_transformed)
pr9_predictions=as.data.table(pr9_predictions)
pr9_predictions$date=product9$event_date

ggplot(pr9_predictions, aes(x=date, y=sold_count))+geom_line()+geom_line(aes(y=fitted),col="red")+ theme_minimal()+
  labs(title="Product 9 Fitted Values ", x="Date", y="Sold Count")
```

